Can BERT learn dialogue-specific phenomena? The case of laughter in dialogue act recognition.

### 2020-07-21 reports/Star-SEM Paper/starsem-paper.tex
typo

For each of the target corpora (SWDA and AMI-DA), we compare four different pre-training conditions: 
The in-domain corpus (\texttt{ID}), consisting of the AMI pre-training corpus for the AMI-DA model and the SWBD pre-traning corpus for the SWDA model; 
the cross-domain corpus (\texttt{CC}), consisting of both the AMI and SWBD pre-training corpora; 
the OpenSubtitles corpus (\texttt{OS});
and finally the standard BERT\textsubscript{BASE} model with no addational pre-training.
As before, we experiment with both frozen and fine-tuned models at the task training stage.

>>>>

For each of the target corpora (SWDA and AMI-DA), we compare four different pre-training conditions: 
The in-domain corpus (\texttt{ID}), consisting of the AMI pre-training corpus for the AMI-DA model and the SWBD pre-traning corpus for the SWDA model; 
the cross-domain corpus (\texttt{CC}), consisting of both the AMI and SWBD pre-training corpora; 
the OpenSubtitles corpus (\texttt{OS});
and finally the standard BERT\textsubscript{BASE} model with no additional pre-training.
As before, we experiment with both frozen and fine-tuned models at the task training stage.
